Mega-analysis of the Interoceptive Accuracy Scale (IAS) Structure and its Subjective Correlates

### 2025-10-24 paper/1_Initial/manuscript.qmd
manuscript updated

<!-- Psychopathologies -->
Autistic traits were generally negatively associated with the IAS, with Imagination (mean r = −.18) showing the most consistent effects across pairings, except for Cough–Sneeze. Most of the significant associations between the full IAS and autistic traits were driven by the first three pairings—Hungry–Thirsty, Bruise–Blood sugar, and Muscles–Pain—which showed the strongest and most reliable negative correlations. Beyond these, effects tended to weaken and often became nonsignificant, particularly for Patterns and Numbers, which did not correlate with any IAS correlate. Borderline Personality was only significantly associated with the Hungry–Thirsty pairing (mean r = −.14).

Lastly, schizotypal traits (SPQ) were also generally negative and non-significant, but several significant associations with the full IAS appeared to be driven by particular pairings.

Autistic traits were generally negatively associated with the IAS, with Imagination (mean r = −.18) showing the most consistent effects across pairings, except for Cough–Sneeze. Across subscales, most associations observed for the full IAS were primarily driven by the first three pairings—Hungry–Thirsty, Bruise–Blood sugar, and Muscles–Pain— which showed the strongest and most reliable negative correlations. Beyond these, effects tended to weaken and often became nonsignificant, particularly for Patterns and Numbers, which did not correlate with any IAS correlate, while Borderline Personality only correlated with the Hungry–Thirsty pairing (mean r = −.14).

@@

Worldview measures were largely null, but certain beliefs showed small yet consistent associations with specific IAS item pairings. Belief in a comprehensible world (“Understandable”) correlated positively with most pairings except Urinate–Defecate and Cough–Sneeze, while beliefs that the world is “Alive” and “Hierarchical” were associated with the full IAS and Hunger–Thirsty, and “Good” was uniquely linked to Muscles–Pain (mean r = .09). For the Lying Profile, only Lying Contextuality showed a notable negative association with the Bruise–Blood sugar pairing (r = −.12).

>>>>

<!-- Psychopathologies -->
Autistic traits were generally negatively associated with the IAS, with Imagination (mean r = −.18) showing the most consistent effects across pairings, except for Cough–Sneeze. Across subscales, most associations observed for the full IAS were primarily driven by the first three pairings—Hungry–Thirsty, Bruise–Blood sugar, and Muscles–Pain— which showed the strongest and most reliable negative correlations. Beyond these, effects tended to weaken and often became nonsignificant, particularly for Patterns and Numbers, which did not correlate with any IAS correlate, while Borderline Personality only correlated with the Hungry–Thirsty pairing (mean r = −.14).

@@

Primal world beliefs measures were largely null, but certain beliefs showed small yet consistent associations with specific IAS item pairings. Belief in a comprehensible world (“Understandable”) correlated positively with most pairings except Urinate–Defecate and Cough–Sneeze, while beliefs that the world is “Alive” and “Hierarchical” were associated with the full IAS and Hunger–Thirsty, and “Good” was uniquely linked to Muscles–Pain (mean r = .09). For the Lying Profile, only Lying Contextuality showed a notable negative association with the Bruise–Blood sugar pairing (r = −.12).
